Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-31 analysis/TAS_memo/memo_TAS_reviewers.Rmd
add information from Xiaomeng

We agree that, given high incompatibility, (1) the bias "detection" rate can be as high as 100% when current bias is low ($b_curr$); and (2) bias detection can be low where current bias is high but bias in historical trials is low. The tradeoff is that, given compatibility, historical strike data increases power that is otherwise low due the limited number of strikes per trial. The advantage of using the power prior: We can adjust the weight of the historical strike data (and therefore type I error) by adjusting $alpha$.

@@

[INSERT] Will get Eric to check this (got a response from Xiaomeng - waiting for follow-up)

>>>>

We agree that, given high incompatibility, (1) the bias "detection" rate can be as high as 100% when current bias is low ($b_curr$); and (2) bias detection can be low where current bias is high but bias in historical trials is low. The tradeoff is that, given compatibility, historical strike data increases power that is otherwise low due the limited number of strikes per trial. The advantage of using the power prior: We can adjust the weight of the historical strike data (and therefore type I error) by adjusting $\alpha$.

@@

This information has been added to the text:

A normal distribution was assumed for the distribution of b. The length of the Markov chain was 110000 and the first 10000 iterations were dropped as burn-in. No thinning was performed, as the correlation was weak and the convergence occured rapidly. Convergence was checked from both traceplots and the Gelman-Rubin statistic. Computation times varies from 0.76 to 1.2 seconds, depending in the amount of data used (current data only _versus_ current and historical data).
